Results

### 2018-03-15 02_analysis.Rmd
PHEW. ANOVA-like modeling with rstanarm and 3-way interactions

```{r load-libraries-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(ggstance)
library(pander)
library(scales)
library(skimr)
library(janitor)
library(here)

source(file.path(here(), "lib", "graphics.R"))
source(file.path(here(), "lib", "pander_options.R"))

@@

  if (is.numeric(x)) {
    numeric_summary(x)
  } else {
    level_summary(x, variable, df)
  }
}
```

@@

## Descriptive statistics

@@

@@

```{r skeleton, eval=FALSE}
# Amount donated by binary likelihood of donation
results %>% group_by(donate_likely_bin) %>% summarize(avg_donation = mean(amount_donate))

# Individual frames
results %>% group_by(crackdown) %>% summarize(avg_donation = mean(amount_donate))
results %>% group_by(issue) %>% summarize(avg_donation = mean(amount_donate))
results %>% group_by(funding) %>% summarize(avg_donation = mean(amount_donate))
results %>% group_by(crackdown, funding) %>% summarize(avg_donation = mean(amount_donate))
results %>% group_by(crackdown, issue) %>% summarize(avg_donation = mean(amount_donate))
results %>% group_by(crackdown, issue, funding) %>% summarize(avg_donation = mean(amount_donate))

# Amount / propensity to donate based on predisposition towards nonprofits
# Amount / propensity to donate based on charitableness
# Amount / propensity to donate based on voluntarism
# Amount / propensity to donate based on political knowledge
# Amount / propensity to donate based on political ideology
# Amount / propensity to donate based on education
# Amount / propensity to donate based on religiosity
# Amount / propensity to donate based on gender
# Amount / propensity to donate based on income
# Amount / propensity to donate based on age

# Control for all those things

```

```{r}
# wilcox.test(donation ~ crackdown, data = results) 
# t.test(donation ~ crackdown, data = results)
```

- Demographic balance across main crackdown condition

- Differences of these across conditions:

    - Mean likelihood
    - Mean likelihood collapsed to binary
    - Mean donation to NGO
    - Mean amount kept for person

- Modeling:

    - donation ~ frames (OLS)
    - likelihood binary  ~ frames (multinomial)
    - likelihood ~ frames (multinomial)
    - those models with controls

>>>>

```{r load-libraries-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(rstanarm)
library(broom)
library(coda)
library(ggstance)
library(pander)
library(scales)
library(skimr)
library(janitor)
library(huxtable)
library(here)

source(file.path(here(), "lib", "graphics.R"))
source(file.path(here(), "lib", "pander_options.R"))
source(file.path(here(), "lib", "modeling.R"))

@@

  if (is.numeric(x)) {
    numeric_summary(x)
  } else {
    level_summary(x, variable, df)
  }
}

if (isTRUE(getOption('knitr.in.progress'))) {
  file_format <- rmarkdown::all_output_formats(knitr::current_input())
} else {
  file_format <- ""
}

print_hux <- function(x) {
  if ("html_document" %in% file_format) {
    print_html(x)
  } else if ("pdf_document" %in% file_format) {
    print_latex(x)
  } else if ("word_document" %in% file_format) {
    print_md(x)
  } else {
    print(x)
  }
}
```

@@

## Descriptive statistics table

@@

## Visualize important variables

@@

## Average likelihood and amount donated across conditions

```{r tbl-results-conditions, results="asis"}
conditions_summary <- bind_rows(group_by(results, crackdown, issue, funding) %>% nest(),
                                group_by(results, crackdown, issue) %>% nest(),
                                group_by(results, crackdown) %>% nest(),
                                results %>% nest()) %>% 
  arrange(crackdown, issue, funding) %>% 
  mutate(summary = data %>%
           map(~ summarize(., pct_likely = table(donate_likely_bin)[["Likely"]] /
                             length(donate_likely_bin),
                           mean_donation = mean(amount_donate, na.rm = TRUE),
                           sd_donation = sd(amount_donate, na.rm = TRUE),
                           N = nrow(.)))) %>% 
  unnest(summary) %>% select(-data)

conditions_summary_clean <- conditions_summary %>% 
  mutate(funding = ifelse(is.na(funding) & !is.na(issue) , "*Total*", as.character(funding)),
         issue = ifelse(is.na(issue) & !is.na(crackdown), "*Total*", as.character(issue)),
         crackdown = ifelse(is.na(crackdown), "*Total*", as.character(crackdown))) %>% 
  group_by(crackdown) %>% 
  mutate(issue = replace(issue, duplicated(issue), NA)) %>% 
  ungroup() %>% 
  mutate(crackdown = replace(crackdown, duplicated(crackdown), NA)) %>% 
  mutate(pct_likely = percent(pct_likely)) %>% 
  rename(`Crackdown condition` = crackdown, `Issue condition` = issue,
         `Funding condition` = funding, `% likely to donate` = pct_likely,
         `Amount donated (mean)` = mean_donation, `Amount donated (sd)` = sd_donation)

conditions_summary_clean %>% pandoc.table()
```

\

# Interpreting models

This is like using ANOVA, but more complex and flexible. Coefficients represent changes from the baseline intercept value.

# Amount donated

## Models

```{r build-models-amount, warning=FALSE, message=FALSE, cache=TRUE}
# Basic interaction models
m_amount_crackdown <- 
  stan_glm(amount_donate ~ crackdown,
           data = results, family = gaussian(),
           prior = student_t(df = 1, location = 0),
           prior_intercept = student_t(df = 1, location = 0),
           chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED)

m_amount_crackdown_issue <- 
  update(m_amount_crackdown, . ~ . + issue + crackdown * issue)

m_amount_crackdown_issue_funding <- 
  update(m_amount_crackdown, . ~ . + 
           issue + funding + crackdown * issue + crackdown * funding + 
           issue * funding + crackdown * issue * funding)

# Interaction models with extra controls
m_amount_crackdown_full <- 
  update(m_amount_crackdown, . ~ . + 
           favor_humanitarian_bin + favor_human_rights_bin + favor_development_bin)

m_amount_crackdown_issue_full <- 
  update(m_amount_crackdown_issue, . ~ . + 
           favor_humanitarian_bin + favor_human_rights_bin + favor_development_bin)

m_amount_crackdown_issue_funding_full <- 
  update(m_amount_crackdown_issue_funding, . ~ . + 
           favor_humanitarian_bin + favor_human_rights_bin + favor_development_bin)

# m_propensity_small <- stan_glm(donate_likely_bin ~ crackdown + issue + funding + 
#                                  crackdown * issue + crackdown * funding + issue * funding +
#                                  crackdown * issue * funding,
#                                data = results, family = binomial(link = "logit"),
#                                prior = student_t(df = 1, location = 0),
#                                prior_intercept = student_t(df = 1, location = 0),
#                                chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED)
```

```{r models-table, results="asis"}
huxreg(m_amount_crackdown, m_amount_crackdown_issue, 
       m_amount_crackdown_issue_funding, 
       m_amount_crackdown_full, m_amount_crackdown_issue_full, 
       m_amount_crackdown_issue_funding_full,
       coefs = clean_coefs_named,
       statistics = model_stats_bayes,
       stars = NULL) %>% 
  print_hux()
```

## Coefficient plot

```{r models-plot}
coefs_amount <- data_frame(model_name = c("Basic model", "Full model"),
                           model = list(m_amount_crackdown_issue_funding,
                                        m_amount_crackdown_issue_funding_full)) %>% 
  mutate(tidy = model %>% map(~ tidyMCMC(., conf.int = TRUE, conf.level = 0.9,
                                         conf.method = "HPDinterval"))) %>% 
  unnest(tidy) %>% 
  left_join(clean_coefs, by = "term") %>% 
  filter(term_clean != "Intercept")

ggplot(coefs_amount, aes(x = estimate, y = fct_rev(term_clean_fct), 
                         color = fct_rev(model_name))) +
  geom_pointrangeh(aes(xmin = conf.high, xmax = conf.low), 
                   position = position_dodgev(height = 0.5)) +
  geom_vline(xintercept = 0) + 
  scale_color_manual(values = c(ngo_red, ngo_blue), 
                     guide = guide_legend(title = NULL, reverse = TRUE)) +
  labs(x = "Posterior median estimate + 90% credible interval", y = NULL) +
  theme_ngos() +
  theme(panel.grid.major.y = element_blank())
```

## Predicted medians

```{r models-predicted}
newdata_conditions <- results %>% 
  expand(nesting(crackdown, issue, funding))

posterior_fit <- posterior_predict(m_amount_crackdown_issue_funding, 
                                   newdata = newdata_conditions,
                                   re.form = NA, draws = 50, seed = BAYES_SEED)

nested_draws <- posterior_fit %>% 
  as_data_frame() %>% 
  gather(id, value) %>% 
  group_by(id) %>%
  nest()

all_posterior_draws <- bind_cols(newdata_conditions, nested_draws) %>% unnest(data)

newdata <- newdata_conditions %>% 
  bind_cols(tidyMCMC(as.mcmc(posterior_fit), conf.int = TRUE, 
                     conf.level = 0.9, conf.method = "HPDinterval"))

ggplot(newdata, aes(y = estimate, x = funding)) + 
  geom_point(data = all_posterior_draws, aes(y = value, x = funding), 
             color = "grey50", size = 1.5, alpha = 0.25) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high)) + 
  scale_y_continuous(labels = dollar) +
  labs(x = "Funding", y = "Average amount donated") +
  coord_cartesian(ylim = c(0, 100)) +
  theme_ngos() +
  facet_wrap(~ crackdown + issue)
```
